The Bolocam Galactic Plane Survey: Survey Description and Data Reduction

### 2009-04-02 methods/ms.tex
changed flagger figures

Figure \ref{fig:PCA_filter}a shows the fraction of flux recovered in the map as a
function of source size for a range of different PCA components subtracted in
the cleaning.  These measurements were produced by inserting simulated gaussian
sources at a range of peak flux densities and sizes spread out through the map
and summing the flux in an ellipse on the final cleaned map.  The median
fraction over all sources of a given size is plotted in the figure.

@@

Figure \ref{fig:deconv_filter}b shows the fraction of flux recovered in the maps
as a function of the deconvolution kernel used to create the astrophysical model
maps.  The differences at large source sizes are not yet well-understood
(!!!!!!), but at the smallest source size, it is evident that a deconvolution
kernel smaller than the source size does not fully recover the source flux.
Therefore we chose a deconvolution kernel smaller than the beam but larger than
the pixel size used.  Figure \ref{fig:Deconvolution} demonstrates the effects of using
both too large and too small a kernel.

@@

\FigureTwo{pca_comparison_l111}{deconvolution_comparison_l111}{The fractional
flux recovered as a function of source size for well-separated Gaussian sources with
the FWHM as indicated. \emph{Left}: 3,7,10,13,16,21,26,31 PCA components subtracted }{fig:PCA_filter}{1.0}

>>>>

Figure \ref{fig:PCA_filter}a shows the fraction of flux recovered in the map as a
function of source size for a range of different PCA components subtracted in
the cleaning.  These measurements were produced by inserting simulated gaussian
sources at a range of peak flux densities and sizes spread out through the map
and summing the flux in an ellipse on the final cleaned map.

@@

Figure \ref{fig:deconv_filter}b shows the fraction of flux recovered in the maps
as a function of the deconvolution kernel used to create the astrophysical model
maps.  The differences at large source sizes are not yet well-understood
(!!!!!!), but at the smallest source size, it is evident that a deconvolution
kernel smaller than the source size does not reliably recover the source flux.
Therefore we chose a deconvolution kernel smaller than the beam but larger than
the pixel size used.  Figure \ref{fig:Deconvolution} demonstrates the effects of using
both too large and too small a kernel.

@@

\FigureTwo{pca_comparison_l111}{deconvolution_comparison_l111}{The fractional
flux recovered as a function of source size for well-separated Gaussian sources with
the FWHM as indicated.
\emph{Left}: 3 (blue),7 (green),10 (yellow) ,13
(orange),16 (red),21 (teal),26 (lime),31 (black) PCA components subtracted.
\emph{Right}: 7.2" (cyan), 14.4" (black), 21.6" (red), 31.2" (green) deconvolution
kernel for 13 PCA components subtracted
}{fig:PCA_filter}{1.0}
